---
output: github_document
---

```{r, eval = FALSE, include = FALSE}
# Print to markdown without distill templating
rmarkdown::render("README.Rmd", output_format = "github_document")
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE
)
```

```{r libraries}
library(dplyr)
```

```{r vars}
# Get URL to repo
url <- desc::desc_get_urls()

# Get Depends, Imports and Suggests
packages <- desc::desc_get_deps()
```

[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.6.0-6666ff.svg)](https://cran.r-project.org/) 
[![Netlify Status](https://api.netlify.com/api/v1/badges/b3a76bf0-ec22-487d-b567-7c2ea7ff4812/deploy-status)](https://app.netlify.com/sites/twitterapi/deploys)
![Build Status](https://img.shields.io/travis/timtrice/distill/master.svg)
![Docker Cloud Build Status](https://img.shields.io/docker/cloud/build/timtrice/distill.svg?style=popout)
[![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/timtrice/distill/master?urlpath=rstudio)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

# `r desc::desc_get_field("Package")` (`r desc::desc_get_version() `)

## `r desc::desc_get_field("Title") `

### Prerequisites

```{r}
packages %>% 
  filter(type == "Depends") %>% 
  select(-.data$type) %>% 
  knitr::kable(
    col.names = c("Package", "Version"), 
    caption = "Version not specified"
  )
```

#### Docker

A Docker image of this project is available for use.

  * [timtrice/distill](https://cloud.docker.com/repository/docker/timtrice/distill)

##### Run

Set $LOCAL to your preferred working directory.

```
LOCAL="/home/Projects/distill"

docker run \
  -dti \
  -e DISABLE_AUTH=true \
  -p 8787:8787 \
  --name distill \
  -v $LOCAL:/home/rstudio/distill \
  timtrice/distill:release
```

##### Shell

```
docker exec -ti distill /bin/bash
```


### Built With

* [R 3.6.0](https://www.r-project.org/) - The R Project for Statistical Computing

### Contributing

Please read [CONTRIBUTING.md](/blob/master/.github/CONTRIBUTING.md) for details on our code of conduct, and the process for submitting pull requests to us.

### Code of Conduct

Please note that the '`r desc::desc_get_field("Package") `' project is released with a [Contributor Code of Conduct](/blob/master/.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

### Versioning

We use [SemVer](http://semver.org/) for versioning. For the versions available, see the [tags on this repository](/tags). 

### Authors

  * `r format(desc::desc_get_author(), include = c("family", "given", "role"), braces = list(family = c("", ","), role = c("(Role(s): ", ")"))) `

### License

This project is licensed under the MIT License - see the [LICENSE.md](/blob/master/LICENSE.md) file for details

### Acknowledgements

`r usethis::use_tidy_thanks() `
